Guided Proofreading of Automatic Segmentations for Connectomics

### 2016-11-23 paper/supplemental/leftcylinder.tex
Supplemental.

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{gfx/cyltrails.pdf}
\caption{Performance comparison of Plaza's focused proofreading and our guided proofreading on the L. Cylinder dataset. All measurements are reported as median VI, the lower the better. We compare automatic selection with threshold and the selection oracle for accepting or rejecting corrections using each method. In all cases, guided proofreading yields better results with fewer corrections.}
\label{fig:cylboxplot}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics[width=.7\linewidth]{gfx/cylboxplot.pdf}
\caption{VI distributions of guided proofreading (GP) and focused proofreading (FP) output across slices of the L. Cylinder dataset, with different error correction approaches. The variation resulting from performance of FP with automatic selection is $7.8\times$ higher than GP (as indicated by the arrow), with median VI of $2.75$ and $SD=0.789$.}
\label{fig:cylboxplot}
\end{figure}

>>>>

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{gfx/datasets.pdf}
\caption{The five different datasets we use for evaluation. The top row shows the first slice of the AC4 and L. Cylinder mouse brain datasets as reported in the paper. The bottom row shows the first slice of the CREMI A/B/C fruit fly datasets which we used for additional experiments.}
\label{fig:datasets}
\end{figure}

We report experiments and results on the L. Cylinder dataset in the paper. Figure~\ref{fig:cyltrails} and~\ref{fig:cylboxplot} visualize the reported results measured as variation of information (VI). We compare automatic selection with threshold and selection oracle using focused proofreading and guided proofreading.

\paragraph{Best possible VI.} The selection oracle using guided proofreading does not reach the best possible VI score. We calculate this score by intersecting the initial segmentation and the ground truth. In theory, the classifier should be able to reach this lower bound. However, the membrane probability maps we use include a 30 pixel frame region because of the used classification patch size. Guided proofreading ignores all segments within this frame region and can not reach the best possible VI in some datasets.

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{gfx/cyltrails.pdf}
\caption{Performance comparison of Plaza's focused proofreading and our guided proofreading on the L. Cylinder dataset as reported in the paper. All measurements are shown as median VI, the lower the better. We compare automatic selection with threshold ($p_t=0.95$, red line) and the selection oracle for accepting or rejecting corrections using each method. Guided proofreading yields better results faster with fewer corrections.}
\label{fig:cyltrails}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{gfx/cylboxplot.pdf}
\caption{VI distributions of guided proofreading (GP) and focused proofreading (FP) output across slices of the L. Cylinder dataset, with different error correction approaches. The variation resulting from performance of FP with automatic selection is $7.8\times$ higher than GP (as indicated by the arrow), with median VI of $2.75$ and $SD=0.789$.}
\label{fig:cylboxplot}
\end{figure}

### 2016-11-23 paper/supplemental/userstudy.tex
Some more supplemental stuff.
Supplemental.

flyers, participant list

@@

Where did users make a mistake?

@@

NASA TLX ANOVA analysis

>>>>

Novice participants were recruited via flyer (figure~\ref{fig:flyer}). An anonymized listing of all participants including demographic information is shown in table~\ref{tab:participants}.

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{gfx/flyer_anon.pdf}
\caption{Participants were recruited with this flyer.}
\label{fig:flyer}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{gfx/NASA_TXL.pdf}
\caption{The NASA-TLX workload index to record subjective responses.}
\label{fig:nasatxl}
\end{figure}

\begin{table}[t]
\caption{The novice participants ($N=20$) of the forced choice user experiment. The table shows sex (20 female), age ($M=30$) and the randomly assigned classifier (focused proofreading as FP, guided proofreading as GP).}%While the training of our classifier is more expensive, testing accuracy is superior. }

\small{
\begin{tabular}{@{}l|c|c|c@{}}
	\toprule
     \textbf{ID} & \textbf{Sex} &  \textbf{Age} & \textbf{Classifier}  \\ \midrule	
S38 &		F & 20 & FP \\
S57&		F & 30 & FP \\ 
S32&		M & 38 & FP \\
S34&		F & 21 & FP \\
S21&		F & 65 & FP \\
S9 &	M & 33 & FP \\
S45 &		M & 28 & FP \\
S31&		M & 27 & FP \\
S24&		F & 21 & FP \\
S6	&	F & 38 & FP \\
S28	&	M&	32& GP \\
S36	&	F&	19& GP \\
S35	&	M&	26& GP \\
S25	&	M&	26& GP \\
S54	&	F&	30& GP \\
S53	&	M&	29& GP \\
S52	&	M	&27& GP \\
S51&		M&	31& GP \\
S200	 &	F	&37& GP \\
S3	 &F&	30 & GP

\end{tabular}
\hspace{2mm}
\hrule
}
\label{tab:participants}
\end{table}

@@

During the user study, participants were asked to accept or reject potential errors and their corrections --- some more difficult than others. Figure~\ref{fig:patches} shows a selection of potential errors and their corrections.

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{gfx/patches.pdf}
\caption{A selection of suggested errors and potential corrections during the forced choice user experiment. The star (*) indicates which choice reduces VI. While all participants were able to correctly choose for patch A, only few were able to correctly choose for patch B and C.}
\label{fig:patches}
\end{figure}

@@

After the experiment, we acquired subjective responses using the NASA-TLX task load index (figure~\ref{fig:nasatxl}). We performed ANOVA to test for statistical significance~\cite{shaffer1995}. Mental, physical, and temporal demands were reported slightly higher for participants using focused proofreading but the analysis did not yield any significance.

\begin{itemize}
\item \textbf{Mental Demand.} Participants using focused proofreading stated a higher mental demand $M=11.5$ ($SD=2.098$) than with guided proofreading $M=8.1$ ($SD=2.003$). This was not statistically significant ($F_{1,18}=3.2574, p=0.3695$).
\item \textbf{Physical Demand.} While naturally physical demand was rated low, participants using focused proofreading stated it slightly higher $M=5.4$ ($SD=2.26$) than with guided proofreading $M=2.9$ ($SD=1.76$). This was not statistically significant ($F_{1,18}=1.7507, p=0.5454$).
\item \textbf{Temporal Demand.} For temporal demand, participants using focused proofreading $M=8.4$ ($SD=1.95$) reported almost equal to guided proofreading $M=8.3$ ($SD=1.99$). This was not statistically significant ($F_{1,18}=0.0033, p=0.9987$).
\item \textbf{Performance.} Here, participants were asked to rate their own performance. All participants rated their performance as pretty well (the lower, the better). For focused proofreading $M=6.8$ ($SD=1.97$) and for guided proofreading $M=7.8$ ($SD=2.04$). This was not statistically significant ($F_{1,18}=0.3091, p=0.8878$).
\item \textbf{Effort.} Participants using focused proofreading stated higher effort $M=13.0$ ($SD=2.336$) than with guided proofreading $M=10.6$ ($SD=2.127$). This was not statistically significant ($F_{1,18}=1.1459, p=0.6599$).
\item \textbf{Frustration.} Participants overall reported low frustration. Reported were $M=5.0$ ($SD=1.90$) using focused proofreading and $M=5.9$ ($SD=185$) using guided proofreading. This was not statistically significant ($F_{1,18}=0.3271, p=0.8818$).
\end{itemize}
